A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-02 02_Materials_and_Methods.Rmd
more about the simulation

To get a better understanding how the correlation coefficient should develop if there were strong correlation between spatial and cultural distance as measured by *burial type* and *burial construction*, a simple simulation was implemented based on the model proposed by @neimanStylisticVariationEvolutionary1995. This simulation assumes a population separated into $g$ groups with a group population of $N_g$ each.

>>>>

To get a better understanding how the correlation coefficient should develop if there were strong correlation between spatial and cultural distance as measured by *burial type* and *burial construction*, a simple simulation was implemented based on the model proposed by @neimanStylisticVariationEvolutionary1995. This simulation assumes a population separated into $g$ groups with a group population of $N_g$ each. At the beginning of the simulation there are $k$ ideas randomly, but equally distributed in this population. With every timestep -- $t$ defines the total number of timesteps -- all individuals learn from an other randomly chosen individual. The probability that this other individual is from an other group equals $m_i$, for the opposite therefore $1-m_i$. The partner group for each individual learning instance is selected randomly following a group interaction probability defined in the matrix $I$.
